Structured Versus Decorated Cospans

### 2021-01-15 cospans.tex
tiny
important observation for proof

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/14

@@

Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
\end{equation}
where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$.
\end{proof}

@@

Moreover, the monoidal unit $I_1$ for ${}_L \lCsp(\inta F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor. For example, the associativity axiom ensuring that the two ways to go from $\lE (M)\ot\lE(M')\ot\lE(M'')$ to $\lE(M\ot M'\ot M'')$ using the above structure isomorphisms are equal, can in fact be deduced from the more general 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$ already discussed in \cite[Theorem 2.7]{Shulman2008}, for the induced global monoidal structure given by $(\phi,\phi_0)$ as discussed in \cref{lem:MonGroth}. Moreover, the earlier associativity axiom for the double functor structure isomorphism $\lE_\odot$ can be deduced using the one for $\lE_\otimes$, by observing that \cref{eq:isomorphismdiag} factors through \cref{eq:Elaxator} as follows
\begin{displaymath}
\begin{tikzcd}[column sep=.4in]
F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(\iota_m)\times F(\iota_{n})"']\ar[dd,bend right=80,out=-90,in=-90,"F(v_m)\times F(v_n)"',"\textstyle\cong"]
\ar[dr,phantom,"{\stackrel{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+n)\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{n})"']  & \\
F(m+n)\times F(m+n)\ar[d,"F(\psi)\times F(\psi)"']\ar[dr,phantom,"\stackrel{\phi_{\psi,\psi}}{\cong}"]\ar[r,"\phi_{m+n,m+n}"'] & F\left((m+n)+(m+n)\right)\ar[r,"F(\nabla)"']\ar[d,"F(\psi+\psi)"']\ar[dr,phantom,"\cong"] & F(m+n)\ar[d,"F(\psi)"] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F((m+_bn)+(m+_bn))\ar[r,"F(\nabla)"'] & F(m+_bn)
\end{tikzcd}
\end{displaymath}
due $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$.

@@

%%% Kenny: Commenting out previous equation.
\begin{comment}
\node (G) at (-1,0.5) {$a$};
\node (H) at (-1,-0.5)  {$b$};
\node (I) at (-2,0.5) {$a$};
\node (J) at (-2,-0.5) {$a$};
\node (E) at (1,1) {$\bot_{b} \in F(b)$};
\node (F) at (1,-1) {$\bot_{b} \in F(b)$};
\node (E') at (-1,1) {$\bot_{a} \in F(a)$};
\node (F') at (-1,-1) {$\bot_{b} \in F(b)$};
\node (L') at (-1,-1.5) {$\tau_{f} \maps F(f)(\bot_a) \to \bot_{b}$};
\node (M) at (2.5,0) {$=$};
\node (N) at (3,0.5) {$a$};
\node (O) at (3,-0.5) {$a$};
\node (P) at (4,0.5) {$b$};
\node (Q) at (4,-0.5) {$b$};
\node (R) at (5,0.5) {$b$};
\node (S) at (5,-0.5) {$b$};
\node (T) at (4,1) {$\bot_{b} \in F(b)$};
\node (U) at (4,-1) {$\bot_{b} \in F(b)$};
\node (V) at (4,-1.5) {$\tau_{b} = 1_{\bot_{b}}$};
(N) edge node[left]{$1$} (O)
(P) edge node[left]{$1$} (Q)
(O) edge node[above]{$f$} (Q)
(S) edge node[above]{$1$} (Q)
\end{comment}

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2021/1/15

@@

Moreover, each fiber $\X_a=F(a)$ obtains a monoidal structure via 
\begin{equation}\label{eq:explicitstructure1}
\otimes_a\maps F(a)\times F(a)\xrightarrow{\phi_{a,a}}F(a+a)\xrightarrow{F(\nabla)}F(a),\quad
I_a\maps\one\xrightarrow{\phi_0}F(0)\xrightarrow{F(!)}F(a)
\end{equation}
where $\nabla$ is the fold map, which is symmetric when $F$ is again via the components of $u_{a,a}$. Also each reindexing functor $f_!=F(f)$ obtains a strong monoidal structure with
\begin{equation}\label{eq:strongreindexing}
\begin{tikzcd}[row sep=.35in]
 F(a)\times F(a)\ar[r,"\phi_{a,a}"]\ar[d,"F(f)\times F(f)"']\ar[dr,phantom,"{\stackrel[\cref{eq:pseudonaturality}]{\phi_{f,f}}{\cong}}"] & 
 F(a+a)\ar[r,"F(\nabla)"]\ar[d,"F(f+f)"description]\ar[dr,phantom,"\cong"] & F(a)\ar[d,"Ff"] \\
 F(b)\times F(b)\ar[r,"\phi_{a,b}"'] & F(b+b)\ar[r,"F(\nabla)"'] & F(b)
\end{tikzcd}
\end{equation}
\end{proof}

@@

Moreover, the monoidal unit $I_1$ for ${}_L \lCsp(\inta F)$ is mapped under $\lE_1$ to the decorated cospan given in \cref{eq:monoidalunitFCsp}, so $\lE_1$ strictly preserves the monoidal unit.
It can be verified that with this structure, $\lE_1$ is also a symmetric monoidal functor. For example, the associativity axiom ensuring that the two ways to go from $\lE (M)\ot\lE(M')\ot\lE(M'')$ to $\lE(M\ot M'\ot M'')$ using the above structure isomorphisms are equal, can in fact be deduced from the more general 2-equivalence between monoidal opfibrations and pseudofunctors into $\MonCat$ already discussed in \cite[Theorem 2.7]{Shulman2008}, for the induced global monoidal structure given by $(\phi,\phi_0)$ as discussed in \cref{lem:MonGroth}. Moreover, the earlier associativity axiom for the double functor structure isomorphism $\lE_\odot$ can be deduced using the one for $\lE_\otimes$, by observing that \cref{eq:isomorphismdiag} factors through \cref{eq:Elaxator} as follows
\begin{displaymath}
\begin{tikzcd}[column sep=.4in]
F(m)\times F(n)\ar[r,"\phi_{m,n}"]\ar[d,"F(\iota_m)\times F(\iota_{n})"']\ar[dd,bend right=80,out=-90,in=-90,"F(v_m)\times F(v_n)"',"\textstyle\cong"]
\ar[dr,phantom,"{\stackrel{\phi_{\iota_m,\iota_n}}{\cong}}"] & F(m+n)\ar[dr]\ar[d,bend left=60, phantom,"\cong"']\ar[d,"F(\iota_m+\iota_{n})"']  & \\
F(m+n)\times F(m+n)\ar[d,"F(\psi)\times F(\psi)"']\ar[dr,phantom,"\stackrel{\phi_{\psi,\psi}}{\cong}"]\ar[r,"\phi_{m+n,m+n}"'] & F\left((m+n)+(m+n)\right)\ar[r,"F(\nabla)"']\ar[d,"F(\psi+\psi)"']\ar[dr,phantom,"\cong"] & F(m+n)\ar[d,"F(\psi)"] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi_{m+_bn,m+_bn}"'] & F((m+_bn)+(m+_bn))\ar[r,"F(\nabla)"'] & F(m+_bn)
\end{tikzcd}
\end{displaymath}
due $\phi$ being a pseudonatural transformation, where $v=\psi\circ\iota$ as in \cref{eq:dcospanscomposition} and the bottom right isomorphism comes from naturality of $\nabla$. Notice that the bottom two-part composite isomorphism is the induced strong monoidal structure on the reindexing functor $F(\psi)$ as in \cref{eq:strongreindexing}.

@@

%%%Christina: if I am not mistaken, John had some comments on how these cospans are written and whether our convention is clear.
